Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-25 krs-survey.tex
Added diagrams of the typology

@@

As previously mentioned, we propose six main categories.
\fxfatal{figure taxonomy}

@@

@@

@@

@@

\subsubsection{Knowledge acquisition and modalities merging}
\label{sect|knowledge-acquisition}

@@

\subsubsection{Ability to automatically create new object instances}
\label{sect|new-instances}

@@

>>>>

% typology diagrams
\usepackage{tikz}
\usetikzlibrary{shapes}

@@

As previously mentioned, we propose six main categories.

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, level distance = 3cm, level 1/.style={sibling distance=5mm}]
    %[edge from parent fork east]
    %every node/.style={fill=black!30,rounded corners},
    %[parent anchor=east,child anchor=west,grow=east,
    %edge from parent/.style={thick,draw}]
    \node {Dimensions}
        child {node {Instantiation}}
        child {node {Integration}}
        child {node {Acquisition}}
        child {node {Reasoning}}
        child {node {Representation}}
        child {node {Expressiveness}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3.5cm]
    \node {\bf Expressiveness}
            child {node {Meta-cognition}}
            child {node {Uncertainty}}
            child {node {Open/Closed world assumption}}
            child {node {Expressive power}}
            child {node {Logic formalism}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3cm]
    \node {\bf Representation}
            child {node {Memory}}
            child {node {Introspection}}
            child {node {Possible Worlds}}
            child {node {Context}}
            child {node {Roles}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 4cm]
    \node {\bf Reasoning}
            child {node {Learning}}
            child {node {Naive physics}}
            child {node {Planning}}
            child {node {Prediction}}
            child {node {Presupposition}}
            child {node {Non-monotonicity}}
            child {node {Uncertainty}}
            child {node {Lazy evaluation}}
            child {node {Structural alteration}}
            child {node {Standard reasoning}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3cm]
    \node {\bf Acquisition}
            child {node {Dynamic instantiation}}
            child {node {Grounding}}
            child {node {Acquisition and fusion}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

\subsubsection{Knowledge acquisition and modalities fusion}
\label{sect|knowledge-acquisition}

@@

\subsubsection{Dynamic instantiation}
\label{sect|new-instances}
Ability to automatically create new object instances

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3cm]
    \node {\bf Integration}
            child {node {Performances}}
            child {node {Monitoring}}
            child {node {Natural Language}}
            child {node {Executive layers}}
            child {node {Sensori-motor}};
\end{tikzpicture}
\end{center}
\end{scriptsize}
